---
title: "Stroke"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: img_heart/1.jpg
    theme: united
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
```


-----------------------------------------------------------------------


```{r global, include = FALSE}
library(glmnet)
library(PerformanceAnalytics)
library(tidymodels)
library(shiny)
library(vip)
library(readr)
library(skimr)
library(DT)
library(wesanderson)
library(shinyWidgets)
heart <- read.csv("stroke copy.csv") %>%
  mutate_if(is.character, as.factor) %>% as.tibble()

# For figure color scheme
hotel.palette <- wes_palette("GrandBudapest2")

```

Sidebar {.sidebar}
===========================================================
`r h3("Objective:")`
`r h3("Predict who have high risk of a stroke.")`
<br>

- - -
<br>

```{r}
fileInput("file1","Choose a CSV file")
```

```{r}
numericRangeInput(inputId = "age",
                  label = "Age Range Input:",
                  value = c(min(heart$age), max(heart$age)))
```

```{r}
sliderInput(
  inputId = "training_slider",
  label   = h4("Training Data Proportion"),
  min     = 0.10,
  max     = 0.90,
  value   = 0.75,
  step    = 0.05,
  ticks   = FALSE
)
```

```{r data.filtered}
heart_filtered <- reactive({
  heart %>%
    filter(age %>% between(left  = input$age[1],
                           right = input$age[2]))
})
```
### Predictors:
1. Gender
2. Age
3. Hypertention
4. Heart disease
5. Ever married
6. Work type
7. Residence type
8. Glucose level
9. BMI
10. Smoking status  

### Outcome:
Stroke(Yes/No)

```{r data.splitting}
# Data splitting and resampling
set.seed(123)

splits <- reactive({
  initial_split(heart_filtered(),
                strata = stroke,
                prop   = input$training_slider)
})


heart_other <- reactive({
  training(splits())
})

heart_test  <- reactive({
  testing(splits())
})


# Create a validation set
set.seed(234)
prop.validation <- .20

val_set <- reactive({
  validation_split(heart_other(),
                   strata = stroke,
                   prop   = 1 - prop.validation)
})
```

```{r create.model}
lr_mod <-
  logistic_reg(mixture = 1, penalty = tune()) %>%
  set_engine("glmnet")

```

```{r create.recipe}

lr_recipe <- reactive({
  recipe(stroke ~ ., data = heart_other()) %>%
    step_dummy(all_nominal(),-all_outcomes()) %>%
    step_zv(all_predictors()) %>%
    step_normalize(all_predictors())
})
```

```{r create.workflow}
lr_workflow <- reactive({
  workflow() %>%
    add_model(lr_mod) %>%
    add_recipe(lr_recipe())
})
```

```{r tuning.grid}
lr_reg_grid <-
  tibble(penalty = 10 ^ seq(-4,-1, length.out = 10))  

# Train and tune the model
lr_tune <- reactive({
  lr_workflow() %>%
    tune_grid(
      resamples = val_set(),
      #rset object
      grid      = lr_reg_grid,
      control   = control_grid(save_pred = TRUE),
      #needed to get data for ROC curve
      metrics   = metric_set(roc_auc)
    )
})


lr_best <- reactive({
  lr_tune() %>% 
  select_best("roc_auc")
})

```

```{r best.workflow}
# Add best validation model to workflow
lr_workflow_best <- reactive({
  finalize_workflow(lr_workflow(),
                    lr_best())       #needs to have the same column name as tune()
})

```

```{r fit.training}
# Inspect fit on entire training data
lr_fit <- reactive({
  lr_workflow_best() %>%
    fit(heart_other())
})  
```

```{r last.fit}
lr_last_fit <- reactive({
  last_fit(lr_workflow_best(),
           splits())
})  

```

```{r confusion.matrix}
lr_conf_mat <- reactive({
  lr_last_fit() %>%
    collect_predictions() %>%
    conf_mat(truth = stroke, estimate = .pred_class)
})  
```

**Correlation matrix chart**
=================================================================
  
```{r}
select(heart, -c("id")) %>%
  keep(is.numeric) %>%
  chart.Correlation(heart[, 2:3],
                    histogram = TRUE,
                    method = c("pearson"))
```

**Data summary**
=================================================================
```{r}
skim(heart)
```

**Validation Summary**
===========================================================


## Column {data-width="500"}

### Data Splitting

**Total Observations:**  
`r reactive(dim(heart_filtered())[1] %>% scales::comma())`

**Training Set:**  
`r reactive(dim(heart_other())[1] %>% scales::comma())`

**Validation Set:**  
`r reactive((dim(heart_other())[1] * prop.validation) %>% scales::comma())`

**Testing Set:**  
`r reactive(dim(heart_test())[1] %>% scales::comma())`




### Data Viewer

```{r}
heart %>%
  slice(1:100) %>%
  datatable(
    options = list(
      searching = FALSE,
      pageLength = 50,
      lengthMenu = c(50, 100)
    ),
    style = "default"
  )

```


## Column {data-width="500"}

### Case Imbalance Check

```{r}
output$case_plot <- renderPlot({
  lr_recipe() %>%
    prep() %>%
    juice() %>%
    ggplot(aes(stroke)) +
    geom_bar(fill = wes_palette("BottleRocket1")[3]) +
    theme_light()
})
plotOutput(outputId = "case_plot")
```

### Workflow

```{r}
# Report workflow with optimized `penalty`
renderPrint(lr_workflow_best())

```

**Classification Results**
===========================================================

## Column {data-width="500"}

### ROC

```{r}

output$lr_auc <- renderPlot({
  lr_tune() %>%
    collect_predictions(parameters = lr_best()) %>%
    roc_curve(stroke, .pred_Yes) %>%
    ggplot(aes(x = 1 - specificity, y = sensitivity)) +
    geom_path(color = hotel.palette[4]) +
    geom_abline(lty = 3, color = hotel.palette[4]) +
    coord_equal() +
    theme_classic()
})

plotOutput(outputId = "lr_auc")


```


### Confusion Matrix

```{r}
# renderPrint(lr_conf_mat() %>% tidy())

output$conf_mat_plot <- renderPlot({
  lr_conf_mat() %>%
    autoplot(type = "heatmap")
})


plotOutput(outputId = "conf_mat_plot")

```


## Column {data-width="500"}

### Variable Importance Plot

```{r, vip.plot}
output$vip_plot <- renderPlot({
  lr_fit() %>%
    pull_workflow_fit() %>%
    vip(
      num_features = 20,
      aesthetics = list(
        color = wes_palette("BottleRocket1")[3],
        fill = wes_palette("BottleRocket1")[3],
        size = 0.3
      )
    ) +
    theme_light()
})

plotOutput(outputId = "vip_plot")

```

### Prediction Metrics

```{r}
output$metrics <- renderTable({
  lr_conf_mat() %>%
    summary() %>%
    select(-.estimator)
})

tableOutput(outputId = "metrics")

```

